### 2015-01-15 ASP.tex
fix broken reference

\begin{enumerate}
\item\textbf{ Modeling steps}
The modeling process can be regarded as a special form of representation whose operations are detailed in \cite{{baral2003knowledge}}. Logical ASP programs follow the strategy of "generate and test". This strategy includes four steps:

>>>>

\begin{enumerate}
\item\textbf{ Modeling steps}
The modeling process can be regarded as a special form of representation whose operations are detailed in \cite{baral2003knowledge}. Logical ASP programs follow the strategy of "generate and test". This strategy includes four steps:
